### 2013-10-01 Paper_Markdown.Rmd
Added site information, changed plotting outputs.

na.samples <- data.frame(size = as.vector(wa.res$sample_size),
                         distance = rep(vals, each = nrow(wa.res$sample_size)),
                         alpha.val = rep(diff(c(-.5,vals)), each = nrow(wa.res$sample_size))+0.005)

@@

ggplot(na.samples, aes(x=distance, y=size)) + geom_point(aes(alpha=alpha.val)) +
  xlab('Analogue Distance') + ylab('Available Samples') +
  theme(text = element_text(size=24, family='serif')) +
  theme_bw() +
  scale_alpha_identity(guide='none')

>>>>

na.samples <- data.frame(site = rep(climate[,1], ncol(wa.res$bias)),
                         size = as.vector(wa.res$sample_size),
                         distance = rep(vals, each = nrow(wa.res$sample_size)),
                         alpha.val = rep(diff(c(-.5,vals)), each = nrow(wa.res$sample_size))+0.005)

@@

ggplot(na.samples, aes(x=distance, y=size, group )) + 
  geom_path(aes(alpha=alpha.val)) +
  xlab('Analogue Distance') + ylab('Available Samples') +
  theme(text = element_text(size=24, family='serif')) +
  theme_bw() +
  scale_alpha_identity(guide='none')
